Stat 400 Project

### 2021-11-30 Stat 400 proj.Rmd
Fixed simulation function so that it works with the new coordinate checker function.

```{r}
#testing github
library(tidyverse)

@@

coord_checker <- function(og_df, new_df, x_dim, y_dim){
  baddies <- NULL
  for(i in 1:nrow(new_df)){
    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'x']) < 0 | as.numeric(new_df[i, 'y']) > y_dim | as.numeric(new_df[i, 'y']) < 0){
      baddies <- append(baddies, i)
    }
  }

@@

  #store new infection status
  new_status <- rep(NA, nrow(current_non_infected))
  newly_infected <- NULL

  #Check to see which suceptable subjects get infected
  #For loop
  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])
      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }else{new_status[j] <- 'S'}
    }
  }

  current_non_infected[newly_infected, 3] <- 'I'
  new_state <- rbind(current_infected, current_non_infected)

  # new_state <- c(new_status, current_infected[,3])
  return(new_state)
}

@@

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 10, 10)
coords
new_status <- infection_status(coords, 2)
new_status

@@

This method is takes another approach. It's somewhat similar to the step function, but this one randomly changes the location of the individuals on a daily basis. Then at that point we gather its neighbors and calculate probability of them becoming infected. We keep track of their state (and update on if they would become infected or not) - then after a certain duration they heal or die. This is computationally easier than having a step function of hundreds of points all moving in space, where we have to calculate distance of each point coming in contact of an infected one.

>>>>

```{r}
library(tidyverse)

@@

coord_checker <- function(og_df, new_df, x_dim, y_dim){
  baddies <- NULL
  for(i in 1:nrow(new_df)){
    if(as.numeric(new_df[i, 'x']) > x_dim | as.numeric(new_df[i, 'y']) > y_dim){
      baddies <- append(baddies, i)
    }
  }

@@

  #store new infection status
  new_status <- rep(NA, nrow(current_non_infected))

  #Check to see which suceptable subjects get infected
  #For loop
  for(i in 1:nrow(current_infected)){
    for(j in 1:nrow(current_non_infected)){
      x_i <- as.numeric(current_infected[i, 'x'])
      y_i <- as.numeric(current_infected[i, 'y'])
      x_s <- as.numeric(current_suceptable[j, 'x'])
      y_s <- as.numeric(current_suceptable[j, 'y'])
      crucial_distance <- rexp(1, 1/mean_crit_dist)
      d <- sqrt((x_i - x_s)^2 + (y_i - y_s)^2)
      if(d <= crucial_distance){
        new_status[j] <- 'I'
      }else{new_status[j] <- 'S'}
    }
  }
  new_state <- c(new_status, current_infected[,3])
  return(new_state)
}

@@

#Testing
df <- starting_vals(100, 2, 10, 10)
len <- get_step_length(df, 10, 10)
dir <- get_step_direction(len)
delts <- get_delts(len, dir)
newdf <- update_coords(df, delts)
coords <- coord_checker(df, newdf, 10, 10)
new_status <- infection_status(coords, 2)
new_status

@@

This method is takes another approach. It's somewhat similar to the step function, but this one randomly changes the location of the individuals on a daily basis. Then at that point we gather its neighbors and calculate probability of them becoming infected. We keep track of those who have come in contact and
